Datasheet for '2019 Revised Supplemental Poverty Measure Research Dataset

### 2024-04-19 paper/datasheet_2019SPM.qmd
datasheet edit

---
title: "Datasheet for '2019 Revised Supplemental Poverty Measure Research Dataset'"
author: 
  - Mary Cheng
thanks: "Code and data are available at: https://github.com/marycx/us_poverty_analysis_2019.git"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Datasheet for '2019 Revised Supplemental Poverty Measure Research Dataset'"
author: 
  - Mary Cheng
thanks: "Code and data are available at: https://github.com/marycx/us_poverty_analysis_2019.git"
date: today
date-format: long
abstract: "Provides access to 2019 Revised Supplemental Poverty Measure Research Dataset about American households' demographic and financial information. This enhances how reproducible research is that uses this data."
format: pdf
number-sections: true
bibliography: references.bib
---
